Summer 2025 ToDo

### 2025-04-21 Relations/Paper/Introduction.tex
Todos started and simple fixes made.

Since Strong Normalization is a central concept in ARS theory,
special attention in our work was given to various incaranations of the concept of well-foundedness in the constructive context.
(Strong normalization is well-foundedness of the converse relation.)
The standard constructive definition does not even allow one to show that SN implies WN, as we discuss in Section \ref{sec:Well-foundedness} and formalize in \texttt{WFCounters.agda}.
  We therefore looked at a number of variations of this notion, their classical counterparts all being logically equivalent. %This gave rise to a rich set of concepts, see Figure \ref{f:wf}.

>>>>

Since Strong Normalization is a central concept in ARS theory,
special attention in our work was given to various incarnations of the concept of well-foundedness in the constructive context.
(Strong normalization is well-foundedness of the converse relation.)
The standard constructive definition does not even allow one to show that SN implies WN, as we discuss in Section \ref{sec:Well-foundedness} and formalize in \texttt{WFCounters.agda}.
  We therefore looked at a number of variations of this notion, their classical counterparts all being logically equivalent. %This gave rise to a rich set of concepts, see Figure \ref{f:wf}.
